---
title       : Predict Gas Use Efficiency
subtitle    : small prediction algorithm use very little car info
author      : LI SUN
job         : Graduate Student
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Motivation

1. Do you want to buy a car with high efficiency of gas usage?
2. Do you want to test if your beloved car is still healthy without eating too much gas?
3. Do you want to show your dream girl/boy that you have a strong mind that you would try things yourself in a scientific way rather than taking numbers that dealer told you?

### Here is the small piece of info which helps you to predict the gas efficiency of the car in question..

--- .class #id 

## Glance at the Original Data
We use mtcars dataset from r to build our model
```{r, echo=FALSE}
head(mtcars)
dim(mtcars)
names(mtcars)
```

---

## Exploratory Analysis I
### Heatmap shows relationships between different variables
```{r, echo=FALSE}
heatmap(scale(as.matrix(mtcars)))
```

---

## Exploratory Analysis II
### Pairwise plots shows correlations between different variables further
```{r, echo=FALSE}
pairs(mtcars, panel=panel.smooth, main="Pairwise scatter plots")
```

---

## Model builder
We will use regression model to build prediction algorithm. We start from throwing all variables into the equation
```{r}
mtcars2 <- mutate(mtcars, cyl=as.factor(cyl), vs=as.factor(vs), am=as.factor(am),
                  gear=as.factor(gear), carb=as.factor(carb))
r0<-lm(mpg~., data=mtcars2)
#summary(r0)$coef
summary(r0)$r.squared
```
Good R squrare!! But due to many varibles are corelating to each other and we will be able to simplify this a lot!

---

### We use step function to serach for more combinations of variable we will use in regression equation
```{r, echo=FALSE, results='hide'}
rsearch<-step(r0, k=log(nrow(mtcars2)))
```
```{r}
summary(rsearch)$coef
summary(rsearch)$r.squared
```
Good enough prediction with only three variables!

---

## Final Conclusion
According to fitted model:
E(mpg) = 9.723 - 2.937 * wt + 1.017 * qsec + 14.079 * am1 - 4.141 * wt * am1
mannual: am1 = 1
automatic: am1 = 0

So if you know your car's weight (wt), 1/4 mile time (qsec), and transmission type, you will be able tell roughly how much miles you car can run with 1 gallon gas!
